### 2023-04-17 final/final-daniel-sanchez.tex
add extra data and run new regressions

However, informality and underemployment\footnote{The Ecuadorian National Institute of Statistics considers ``adequate employment'' as people with a job who earn labour income equal to or greater than the minimum wage on an hourly basis. In this sense, underemployment in this paper is considered as any employment which does not comply with this condition.}in this labour market have been shown to be historically high \parencite{Meneses.2021, Chavez.2012, Mendoza.2020}. It has been determined that minimum wage increases in Ecuador (which have been frequent and substantial) have had no effect on employment levels due to high-level of non-compliance and informality in the labour market \parencite{Canelas.2014}. Further, Ecuador has been shown to have one of the most cumbersome labour market legislations in the region \parencite{MacIsaac.1997}, whose effect is attenuated by smaller base earnings over which benefits are paid.

Not only the labour market is highly regulated in the country: the business environment in Ecuador is cumbersome, including several artificial costs which could create inefficiencies. Ecuador constantly ranks very low in terms of property rights, judicial transparency and economic freedom. Its low standing in economic freedom responds to a flawed and corrupt judiciary, characterized by inefficiency and difficulty to start a business \textcite{Euromonitor.2022}. Further, an unstable economic and political environment after the election of conservative businessman Guillermo Lasso not long after a decade-long leftist regime has taken a toll on the government's financing capabilities. The political instability has also made the deregulation of labour markets difficult only one set of market-friendly policies set forth by the new president have been passed, the labour market reform being immediately rejected by a strong opposing majority in Congress. Thus, other types of reforms which indirectly target the labour market would be welcome.

The SAS reform, enacted in May 2020, allowed a new type of legal business to exist, which also exists in other countries in the region. This type of business is known to be much less burdensome than other types of companies like anonymous societies or limited liability companies. A SAS business can be created with lower monetary and time costs (notarization, registering, etc.) as well as with lower amounts of capital contributions. It is sensible to believe that the reform was unexpected and exogeneous since, while the law that allowed for this reform came into force in early 2020, the law did not specifically plan for the creation of this type of business, only allowed for its creation under the Ecuadorian corporate law. Further, \textcite{CaminoMogro.2022} find causal evidence that this reform was effective in formalizing/creating businesses and in reducing time and money entry costs. However, the effects of the policy in the labour market have not been studied so far.

\section{Methodology}
\subsection{Data}
I construct a province-month panel dataset of the country with variables stemming from various government sources. The variable of interest is the log of total job contracts registered with Social Security. Table \ref{tab:sources} defines all variables used in the paper along with their source. Any kind of job contract which is registered in Social Security is thought to be formal, as Social Security formalization implies that all employment benefits mandated by the Ecuadorian Labour Code are being met by the employer and the government.
\begin{table}[h]
\caption{Mean values by year}
\label{tab:descrip}
\centering

\begin{tabular}[t]{lrrrrr}
\toprule
  & 2018 & 2019 & 2020 & 2021 & 2022\\
\midrule
Formal jobs & \num{10.24} & \num{10.23} & \num{10.16} & \num{10.08} & \num{10.14}\\
Active businesses & \num{2.24} & \num{2.52} & \num{2.42} & \num{2.84} & \num{3.05}\\
Remote workers & \num{0.93} & \num{1.37} & \num{3.15} & \num{2.37} & \num{1.79}\\
Registered tax contributors & \num{6.48} & \num{6.53} & \num{6.02} & \num{6.38} & \num{6.39}\\
Reported sales & \num{18.80} & \num{18.81} & \num{18.71} & \num{18.81} & \num{18.96}\\
Total COVID-19 cases &  &  & \num{6.41} & \num{6.47} & \num{6.43}\\
Total COVID-19 deaths &  &  & \num{2.97} & \num{2.64} & \num{1.96}\\
Thefts & \num{4.57} & \num{4.59} & \num{4.24} & \num{4.38} & \num{4.57}\\
Homicides & \num{1.10} & \num{1.18} & \num{1.25} & \num{1.46} & \num{1.91}\\
Transit Accidents & \num{1.04} & \num{1.10} & \num{1.01} & \num{0.92} & \num{1.14}\\
\bottomrule
\end{tabular}

@@

\section{Results}
Table \ref{tab:regseg} displays OLS estimation results for the empirical model specified in Equation \ref{eqn:seg} and Table \ref{app:seg} in Appendix B presents the same results but with HAC standard errors. Model 1 below estimates a naive segmented regression model considering only the treatment dummy interacted with the time trend. The interaction between the time trend and the treatment dummy is not statistically significant, which is evidence for a null effect of the SAS reform on employment. The negative and statistically significant coefficient on the treatment dummy means that, as time passed, there seemed to be a negative trend after the date of the policy. Model 2 estimates the same naive model but now considering province fixed effects, which control for all province-specific factors which affect formal employment yet stay constant through time. In this case, including the FE controls renders the interaction term positive and significant. Potentially, the $\hat{\delta_1}$ coefficient in Model 1 is biased toward zero as it is possible that some provinces with less economic activity suffered from staggered pandemic effects after the policy change. If other provinces saw a positive effect, it would mean that the average effect on the naive regression would be biased toward zero. 
\begin{table}[htbp!]
\caption{Segmented Regressions}
\label{tab:regseg}

\begin{tabular}[t]{lcccccc}
\toprule
  & (1) & (2) & (3) & (4) & (5) & (6)\\
\midrule
Time & \num{0.003}* & \num{0.000} & \num{0.000} & \num{-0.004}*** & \num{0.000} & \num{0.001}\\
 & (\num{0.002}) & (\num{0.001}) & (\num{0.001}) & (\num{0.001}) & (\num{0.001}) & (\num{0.001})\\
Time (quadratic) &  &  &  & \num{0.000}*** & \num{0.000} & \num{0.011}***\\
 &  &  &  & (\num{0.000}) & (\num{0.000}) & \vphantom{1} (\num{0.001})\\
Treatment & \num{-0.237}*** & \num{-0.152}*** & \num{-0.119}*** & \num{-0.073}*** & \num{0.001} & \num{0.025}***\\
 & (\num{0.030}) & (\num{0.026}) & (\num{0.014}) & (\num{0.016}) & (\num{0.011}) & (\num{0.006})\\
Interaction & \num{0.001} & \num{0.003}*** & \num{0.001} &  &  & \\
 & (\num{0.002}) & (\num{0.001}) & (\num{0.001}) &  &  & \\
Interaction (quadratic) &  &  &  & \num{0.000}*** & \num{0.000} & \num{-0.011}***\\
 &  &  &  & (\num{0.000}) & (\num{0.000}) & (\num{0.001})\\
WFH workers &  &  & \num{0.001} & \num{0.001} & \num{0.000} & \num{0.000}\\
 &  &  & (\num{0.002}) & (\num{0.002}) & (\num{0.001}) & (\num{0.001})\\
Thefts &  &  & \num{0.019} & \num{0.011} & \num{0.015}* & \num{0.000}\\
 &  &  & (\num{0.017}) & (\num{0.017}) & (\num{0.008}) & (\num{0.007})\\
Homicides &  &  & \num{0.002} & \num{0.001} & \num{0.001}** & \num{0.001}\\
 &  &  & (\num{0.004}) & (\num{0.004}) & (\num{0.001}) & (\num{0.002})\\
Tax contributors &  &  & \num{0.001} & \num{-0.001}* & \num{0.002}** & \num{0.001}\\
 &  &  & (\num{0.001}) & (\num{0.001}) & (\num{0.001}) & (\num{0.001})\\
Sales &  &  & \num{0.039}** & \num{0.033}** & \num{0.007} & \num{0.003}\\
 &  &  & (\num{0.016}) & (\num{0.013}) & (\num{0.004}) & (\num{0.006})\\
Transit Accidents &  &  & \num{0.003} & \num{0.002} & \num{-0.001} & \num{-0.002}\\
 &  &  & (\num{0.002}) & (\num{0.002}) & (\num{0.001}) & (\num{0.002})\\
Businesses &  &  &  &  & \num{0.008}*** & \num{0.006}\\
 &  &  &  &  & (\num{0.002}) & (\num{0.004})\\
Lag of jobs &  &  &  &  & \num{0.950}*** & \num{0.886}***\\
 &  &  &  &  & (\num{0.029}) & (\num{0.061})\\
COVID-19 cases &  &  &  &  &  & \num{0.000}\\
 &  &  &  &  &  & (\num{0.002})\\
COVID-19 deaths &  &  &  &  &  & \num{-0.001}\\
 &  &  &  &  &  & (\num{0.001})\\
\midrule
$N$ & \num{1327} & \num{1327} & \num{439} & \num{439} & \num{439} & \num{239}\\
Adj. $R^2$ & \num{0.00071} & \num{0.99835} & \num{0.99955} & \num{0.99960} & \num{0.99994} & \num{0.99991}\\
Adj. Within $R^2$ &  & \num{0.46583} & \num{0.74803} & \num{0.77687} & \num{0.96416} & \num{0.85563}\\
AIC & \num{4708.41} & \num{-3771.83} & \num{-1851.95} & \num{-1904.38} & \num{-2705.34} & \num{-1398.01}\\
BIC & \num{4729.17} & \num{-3631.68} & \num{-1733.50} & \num{-1781.85} & \num{-2574.64} & \num{-1283.29}\\
Province FE &  & X & X & X & X & X\\
\bottomrule
\end{tabular}

@@

Models 3 through 5 consider a variety of controls and alternative specifications to check for the robustness of Model 2's results. Model 3 adds a variety of controls. WFH workers will control for temporary waves of COVID-19 contagions. The amount of transit accidents work to that effect as well. Further, thefts and homicides should control for any kind of effect of the recent violence wave that has stricken the country beginning 2020 and intensified during 2022. Both the amount of firm-type tax contributors and reported sales to the tax authority control for economic fluctuations. The effect is only significant when considering a quadratic trend of the time variable (Model 4), and in even in such case, the magnitude of the effect is very small: on average, the SAS reform created 0.041533\% more Social Security-registered jobs.

Model 5 performs a robustness check and controls for the natural log of active businesses. The theoretical model predicts that employment will be a result of a higher number of businesses entering the economy, which means that controlling for business creation over time should render the effect of the policy on employment statistically insignificant. Further, a positive significance of the business coefficient should be seen. Both of these results are seen in the data, which is evidence in favour of the theoretical model. Further, I take into account the possibility of an autoregressive process by adding a lag of the dependent variable, which is statistically significant, supporting the possibility of an AR(1) process.

In Model 6 I take into account COVID-19 cases and deaths to control for all fluctuations caused by the pandemic in employment, however, I must then restrict to a shorter horizon and perhaps ignore the underlying trend of employment in the data. In this case, I also include businesses and the lagged term. It would be again expected that the effect of the policy on employment is insignificant, however, the model finds a negative effect of the policy on employment. This could mean that after the policy implementation there may be unobserved variables affecting employment. Note that all results with HAC standard errors are similar.

Figure \ref{fig:event} displays the event study plots for four different specifications which follow Equation \ref{eqn:event}. The figures plot the coefficients of each period dummy, and the reference level is May 2020. The leftmost figures consider the period dummies and the controls used for Model 3 in Table \ref{tab:regseg}. The rightmost figures consider the amount of active businesses prevalent at the province-level as a robustness check: it would be expected that all post-policy change effects are zero if the SAS reform affects employment through business creation.

The event study plots cast doubt on the results obtained with the segmented regression specifications. First, the pre-policy change coefficients are in almost all cases statistically different from zero, which suggests that an assumption for segmented regression analysis may be faulty, given that other unobserved factors may have changed along with the policy. Further, it is unsure whether or not the policy affected employment through business creation only given that the rightmost figures show that the post-policy change dummies are statistically different from zero. This means that even after controlling for businesses at the province-level, there is a significant difference between employment at post-policy periods relative to the period where the policy was enacted. Only the case where I restrict for 2020-2022 data and include COVID-19 outcomes as controls there is evidence that the effect of the policy on employment is zero after controlling for business creation, which implies the theoretical model motivating the analysis is sound. Nevertheless, since this result is sensitive to functional form as well as the choice of sample, more empirical tests are needed to confirm that the effect of the policy change, in the framework that I've established here, indeed affects employment only through business creation.

@@

\section*{Appendix B: Table \ref{tab:regseg}'s results with HAC standard errors}
\label{sec:appb}
\renewcommand{\thetable}{B.\arabic{table}} % set the table counter to use "A" as the section label
\caption{Segmented regressions with HAC standard errors}
\label{app:seg}

\begin{tabular}[t]{lcccccc}
\toprule
  & (1) & (2) & (3) & (4) & (5) & (6)\\
\midrule
Time & \num{0.003} & \num{0.000} & \num{0.000} & \num{-0.004}*** & \num{0.000} & \num{0.001}\\
 & (\num{0.006}) & (\num{0.001}) & (\num{0.000}) & (\num{0.001}) & (\num{0.000}) & (\num{0.001})\\
Time (quadratic) &  &  &  & \num{0.000}*** & \num{0.000} & \num{0.011}***\\
 &  &  &  & (\num{0.000}) & (\num{0.000}) & \vphantom{1} (\num{0.003})\\
Treatment & \num{-0.237}*** & \num{-0.152}*** & \num{-0.119}*** & \num{-0.073}*** & \num{0.001} & \num{0.025}*\\
 & (\num{0.040}) & (\num{0.022}) & (\num{0.011}) & (\num{0.014}) & (\num{0.006}) & (\num{0.014})\\
Interaction & \num{0.001} & \num{0.003}*** & \num{0.001} &  &  & \\
 & (\num{0.006}) & (\num{0.001}) & (\num{0.001}) &  &  & \\
Interaction (quadratic) &  &  &  & \num{0.000}*** & \num{0.000} & \num{-0.011}***\\
 &  &  &  & (\num{0.000}) & (\num{0.000}) & (\num{0.003})\\
WFH workers &  &  & \num{0.001} & \num{0.001} & \num{0.000} & \num{0.000}\\
 &  &  & (\num{0.002}) & (\num{0.002}) & (\num{0.000}) & (\num{0.001})\\
Thefts &  &  & \num{0.019} & \num{0.011} & \num{0.015}*** & \num{0.000}\\
 &  &  & (\num{0.011}) & (\num{0.011}) & (\num{0.004}) & (\num{0.006})\\
Homicides &  &  & \num{0.002} & \num{0.001} & \num{0.001} & \num{0.001}\\
 &  &  & (\num{0.003}) & (\num{0.003}) & (\num{0.001}) & (\num{0.002})\\
Tax contributors &  &  & \num{0.001} & \num{-0.001} & \num{0.002}*** & \num{0.001}\\
 &  &  & (\num{0.001}) & (\num{0.001}) & (\num{0.001}) & (\num{0.001})\\
Sales &  &  & \num{0.039}*** & \num{0.033}*** & \num{0.007}** & \num{0.003}\\
 &  &  & (\num{0.011}) & (\num{0.010}) & (\num{0.003}) & (\num{0.004})\\
Transit Accidents &  &  & \num{0.003} & \num{0.002} & \num{-0.001} & \num{-0.002}\\
 &  &  & (\num{0.002}) & (\num{0.002}) & (\num{0.001}) & (\num{0.002})\\
Businesses &  &  &  &  & \num{0.008}*** & \num{0.006}**\\
 &  &  &  &  & (\num{0.002}) & (\num{0.003})\\
Lag of jobs &  &  &  &  & \num{0.950}*** & \num{0.886}***\\
 &  &  &  &  & (\num{0.031}) & (\num{0.056})\\
COVID-19 cases &  &  &  &  &  & \num{0.000}\\
 &  &  &  &  &  & (\num{0.002})\\
COVID-19 deaths &  &  &  &  &  & \num{-0.001}\\
 &  &  &  &  &  & (\num{0.001})\\
\midrule
$N$ & \num{1327} & \num{1327} & \num{439} & \num{439} & \num{439} & \num{239}\\
Adj. $R^2$ & \num{0.00071} & \num{0.99835} & \num{0.99955} & \num{0.99960} & \num{0.99994} & \num{0.99991}\\
Adj. Within $R^2$ &  & \num{0.46583} & \num{0.74803} & \num{0.77687} & \num{0.96416} & \num{0.85563}\\
AIC & \num{4708.41} & \num{-3771.83} & \num{-1851.95} & \num{-1904.38} & \num{-2705.34} & \num{-1398.01}\\
BIC & \num{4729.17} & \num{-3631.68} & \num{-1733.50} & \num{-1781.85} & \num{-2574.64} & \num{-1283.29}\\
Province FE &  & X & X & X & X & X\\
\bottomrule
\end{tabular}

>>>>

However, informality and underemployment\footnote{The Ecuadorian National Institute of Statistics considers ``adequate employment'' as people with a job who earn labour income equal to or greater than the minimum wage on an hourly basis. In this sense, underemployment in this paper is considered as any employment which does not comply with this condition.} in this labour market have been shown to be historically high \parencite{Meneses.2021, Chavez.2012, Mendoza.2020}. Further, minimum wage increases in Ecuador (which have been frequent and substantial) have had no effect on employment levels due to high-level of non-compliance and informality in the labour market \parencite{Canelas.2014}. Further, Ecuador has been shown to have one of the most cumbersome labour market legislations in the region \parencite{MacIsaac.1997}, whose effect is attenuated by smaller base earnings over which benefits are paid.

Not only the labour market is highly regulated in the country: the business environment in Ecuador is cumbersome, including several regulatory costs which could create inefficiencies. Ecuador constantly ranks very low in terms of property rights, judicial transparency and economic freedom, which may respond to a flawed and corrupt judiciary, characterized by inefficiency and difficulty to start a business \textcite{Euromonitor.2022}. Further, an unstable economic and political environment after the election of conservative businessman Guillermo Lasso not long after a decade-long leftist regime has taken a toll on the government's financing capabilities. The political instability has also made the deregulation of labour markets difficult: only one set of market-friendly policies set forth by the new president have been passed, the labour market reform being immediately rejected by a strong opposing majority in Congress. Thus, other types of reforms which indirectly target the labour market would be welcome.

There are several legal figures under which a firm may operate on the Ecuadorian economy. If the firm is fully informal, we may not observe any kind of registry of their economic activity. Most of underemployment comes from this kind of firms, where household members become informal entrepreneurs by selling services or goods informally. However, \textit{partially formal} employment is quite prevalent, and in this scheme the figure of a ``tax contributor'' becomes relevant. There are differentiated tax figures for entrepreneurs in Ecuador: most fall under a ``microbusiness'' which need not establish a formal company but merely have a \textit{registro único de contribuyente}\footnote{Unique contributor registration} (RUC), which is a tax identificator number which allows those registered to issue invoices and pay value-added tax. Having a RUC is relatively low cost compared to establishing a company, yet there is a revenue limit: if any firm exceeds such limit, it must pay more taxes or constitute a legal company figure. A lot of informal work comes from these types of legal figures, which creates the need to control for tax contributor changes across provinces and time, which is possible due to SRI data.

The SAS reform, enacted in May 2020, allowed a new type of legal business to exist, which also exists in other countries in the region. This type of business is known to be much less burdensome than other types of companies like anonymous societies or limited liability companies. A SAS business can be created with lower monetary and time costs (notarization, registering, etc.) as well as with lower amounts of capital contributions. The SAS company would allow an informal firm working under a RUC scheme to easily transition to a formal company. It is sensible to believe that the reform was unexpected and exogenous since, while the law that allowed for this reform came into force in early 2020, the law did not specifically plan for the creation of this type of business, only allowed for its creation under corporate law. Further, \textcite{CaminoMogro.2022} find causal evidence that this reform was effective in formalizing/creating businesses and in reducing time and money entry costs. However, the effects of the policy in the labour market have not been studied so far.

\section{Methodology}
\subsection{Data}
I construct a province-month panel dataset of the country with variables stemming from various government sources. The variables of interest are the natural logarithms of (1) total job contracts registered with Social Security and (2) total job contracts registered under the unique Ecuadorian Labour System (SUT, for its initials in Spanish). The latter is a more reduced measure of formal employment, but it should move with Social Security job contracts.

Table \ref{tab:sources} in the Appendix defines all variables used in the paper along with their source. Any kind of job contract which is registered in Social Security is thought to be formal, as Social Security formalization implies that all employment benefits mandated by the Ecuadorian Labour Code are being met by the employer and the government. The same applies for formal job contracts registered under SUT. 
\begin{table}[h]
\caption{Mean values by year}
\label{tab:descrip}
\centering

\begin{tabular}[t]{lrrrrr}
\toprule
  & 2018 & 2019 & 2020 & 2021 & 2022\\
\midrule
Formal jobs & \num{10.24} & \num{10.23} & \num{10.16} & \num{10.08} & \num{10.14}\\
Formal jobs (SUT) &  &  & \num{5.24} & \num{5.71} & \num{6.39}\\
Active businesses & \num{2.24} & \num{2.52} & \num{2.42} & \num{2.84} & \num{3.05}\\
Remote workers & \num{0.93} & \num{1.37} & \num{3.15} & \num{2.37} & \num{1.79}\\
Registered tax contributors & \num{10.54} & \num{10.61} & \num{10.69} & \num{10.76} & \num{10.87}\\
Reported sales & \num{18.80} & \num{18.81} & \num{18.71} & \num{18.81} & \num{18.96}\\
Total COVID-19 cases &  &  & \num{6.41} & \num{6.47} & \num{6.43}\\
Total COVID-19 deaths &  &  & \num{2.97} & \num{2.64} & \num{1.96}\\
Thefts & \num{4.57} & \num{4.59} & \num{4.24} & \num{4.38} & \num{4.57}\\
Homicides & \num{1.10} & \num{1.18} & \num{1.25} & \num{1.46} & \num{1.91}\\
Transit Accidents & \num{1.04} & \num{1.10} & \num{1.01} & \num{0.92} & \num{1.14}\\
Inscriptions & \num{6.36} & \num{6.51} & \num{5.83} & \num{6.08} & \num{6.29}\\
Suspensions & \num{6.48} & \num{6.53} & \num{6.02} & \num{6.38} & \num{6.39}\\
Total mobility &  &  & \num{-19.42} & \num{9.20} & \num{37.08}\\
\bottomrule
\end{tabular}

@@

\section{Results}
Table \ref{tab:regseg} displays OLS estimation results for the empirical model specified in Equation \ref{eqn:seg} and Table \ref{app:seg} in Appendix B presents the same results but with HAC standard errors. Model 1 below estimates a naive segmented regression model considering only the treatment dummy interacted with the time trend. The interaction between the time trend and the treatment dummy is not statistically significant. The negative and statistically significant coefficient on the treatment dummy means that, as time passed, there seemed to be a negative trend after the date of the policy. Model 2 estimates the same naive model but now considering province fixed effects, which control for all province-specific factors which affect formal employment yet stay constant through time. In this case, including fixed effects renders the interaction term positive and significant. Potentially, the $\hat{\delta_1}$ coefficient in Model 1 is biased toward zero as it is possible that some provinces with less economic activity suffered from staggered pandemic effects after the policy change. If other provinces saw a positive effect, it would mean that the average effect on the naive regression would be biased toward zero.
\begin{table}[htbp!]
\caption{Segmented Regressions}
\label{tab:regseg}

\begin{tabular}[t]{lcccccc}
\toprule
  & (1) & (2) & (3) & (4) & (5) & (6)\\
\midrule
Time & \num{0.003}* & \num{0.000} & \num{0.001} & \num{-0.004}*** & \num{0.001} & \num{0.001}\\
 & (\num{0.002}) & (\num{0.001}) & (\num{0.001}) & (\num{0.001}) & (\num{0.001}) & (\num{0.001})\\
Time (quadratic) &  &  &  & \num{0.000}*** & \num{0.000} & \num{0.012}***\\
 &  &  &  & (\num{0.000}) & (\num{0.000}) & \vphantom{1} (\num{0.002})\\
Treatment & \num{-0.237}*** & \num{-0.152}*** & \num{-0.120}*** & \num{-0.074}*** & \num{-0.007} & \num{0.031}***\\
 & (\num{0.030}) & (\num{0.026}) & (\num{0.014}) & (\num{0.017}) & (\num{0.009}) & (\num{0.009})\\
Interaction & \num{0.001} & \num{0.003}*** & \num{0.001} &  &  & \\
 & (\num{0.002}) & (\num{0.001}) & (\num{0.001}) &  &  & \\
Interaction (quadratic) &  &  &  & \num{0.000}*** & \num{0.000} & \num{-0.012}***\\
 &  &  &  & (\num{0.000}) & (\num{0.000}) & (\num{0.002})\\
WFH workers &  &  & \num{0.001} & \num{0.001} & \num{0.000} & \num{0.000}\\
 &  &  & (\num{0.002}) & (\num{0.002}) & (\num{0.001}) & (\num{0.001})\\
Thefts &  &  & \num{0.020} & \num{0.012} & \num{0.008} & \num{-0.001}\\
 &  &  & (\num{0.017}) & (\num{0.017}) & (\num{0.007}) & (\num{0.008})\\
Homicides &  &  & \num{0.003} & \num{0.002} & \num{0.001}* & \num{0.001}\\
 &  &  & (\num{0.004}) & (\num{0.004}) & (\num{0.001}) & (\num{0.002})\\
Tax contributors &  &  & \num{-0.081} & \num{-0.094} & \num{-0.041} & \num{-0.095}*\\
 &  &  & (\num{0.058}) & (\num{0.068}) & (\num{0.035}) & (\num{0.054})\\
Sales &  &  & \num{0.039}** & \num{0.033}** & \num{0.006} & \num{0.000}\\
 &  &  & (\num{0.017}) & (\num{0.013}) & (\num{0.004}) & (\num{0.005})\\
Transit Accidents &  &  & \num{0.003} & \num{0.002} & \num{-0.001} & \num{-0.002}\\
 &  &  & (\num{0.002}) & (\num{0.002}) & (\num{0.001}) & (\num{0.002})\\
Businesses &  &  &  &  & \num{0.006}** & \num{0.007}\\
 &  &  &  &  & (\num{0.003}) & (\num{0.004})\\
Lag of jobs &  &  &  &  & \num{0.942}*** & \num{0.870}***\\
 &  &  &  &  & (\num{0.031}) & (\num{0.065})\\
COVID-19 cases &  &  &  &  &  & \num{0.000}\\
 &  &  &  &  &  & \vphantom{1} (\num{0.002})\\
COVID-19 deaths &  &  &  &  &  & \num{-0.001}\\
 &  &  &  &  &  & (\num{0.002})\\
Inscriptions &  &  &  &  & \num{0.007}*** & \num{-0.004}\\
 &  &  &  &  & (\num{0.002}) & \vphantom{1} (\num{0.003})\\
Suspensions &  &  &  &  & \num{0.002} & \num{0.004}\\
 &  &  &  &  & (\num{0.002}) & (\num{0.003})\\
Mobility &  &  &  &  &  & \num{0.000}\\
 &  &  &  &  &  & (\num{0.000})\\
\midrule
$N$ & \num{1327} & \num{1327} & \num{439} & \num{439} & \num{438} & \num{236}\\
Adj. $R^2$ & \num{0.00071} & \num{0.99835} & \num{0.99955} & \num{0.99961} & \num{0.99994} & \num{0.99991}\\
Adj. Within $R^2$ &  & \num{0.46583} & \num{0.74985} & \num{0.77949} & \num{0.96697} & \num{0.85451}\\
AIC & \num{4708.41} & \num{-3771.83} & \num{-1855.13} & \num{-1909.57} & \num{-2732.13} & \num{-1380.83}\\
BIC & \num{4729.17} & \num{-3631.68} & \num{-1736.68} & \num{-1787.04} & \num{-2593.33} & \num{-1263.06}\\
Province FE &  & X & X & X & X & X\\
\bottomrule
\end{tabular}

@@

Models 3 through 5 consider a variety of controls and alternative specifications to check for the robustness of Model 2's results. Model 3 adds a variety of controls. WFH workers will control for temporary waves of COVID-19 contagions. The amount of transit accidents work to that effect as well. Further, thefts and homicides should control for any kind of effect of the recent violence wave that has stricken the country beginning 2020 and intensified during 2022. Both the amount of firm-type tax contributors and reported sales to the tax authority control for economic fluctuations. The interaction term is only significant when considering a quadratic trend of the time variable (Model 4), and in even in such case, the magnitude of the effect is very small: on average, the SAS reform created 0.041766\% more Social Security-registered jobs.

Model 5 performs a robustness check and controls for the natural log of active businesses as well as inscriptions and suspensions. The theoretical model predicts that employment will be a result of a higher number of businesses entering the economy, which means that controlling for business creation over time should render the effect of the policy on employment statistically insignificant. Further, a positive significance of the business coefficient should be seen. Endogenous administrative efforts to crack down on tax evasion can be controlled by inscriptions and suspensions of tax contributors, as well as potential spillover effects of the policy on RUC informal firms. Further, I take into account the possibility of an autoregressive process by adding a lag of the dependent variable in this model, which is statistically significant. The signs on the coefficients of business creation and the interaction do support the model: the effects of businesses and new tax contributors are statistically significant and the interaction term is statistically significant.

In Model 6 I take into account COVID-19 cases and deaths to control for all fluctuations caused by the pandemic in employment, however, I must then restrict to a shorter horizon and perhaps ignore the underlying trend of employment in the data. I can also control for changes in mobility by using Google Mobility reports. In this case, I also include businesses and the lagged term. In this case, a negative interaction term is found, which could mean that after controlling for changes in employment due to new businesses and tax contributors, after May 2020 less formal employment was created. This is intuitive when noting that May 2020 was the first month after full lockdown on April, so it can be said that the data support the theoretical data.

Figure \ref{fig:event} displays event study plots for four different specifications which follow Equation \ref{eqn:event}. The figures plot the coefficients of each period dummy, and the reference level is May 2020. The leftmost figures consider the period dummies and the controls used for Model 3 in Table \ref{tab:regseg}. The rightmost figures consider the amount of active businesses, inscriptions and suspensions prevalent as a robustness check: it would be expected that all post-policy change effects are zero if the SAS reform affects employment through business creation.

The event study plots cast doubt on the results obtained with the segmented regression specifications. First, the pre-policy change coefficients are statistically different from zero in the specifications that do not consider COVID-19 controls. This suggests that an assumption for segmented regression analysis may be faulty, given that other unobserved factors may have changed along with the policy. The COVID-19 setting proves a better environment for testing the effect of the policy, which does show zero pre-treatment effects, however, the plots show that there was no overall effect on employment after the policy change. The rightmost event study plots allow to test the fit of the model with the data. While it is seen that all post-policy dummies are not statistically different from zero, the pre-change dummies are also not statistically different from zero, which casts doubt on the validity of the event study assumptions.

The results discussed here are robust to using HAC standard errors. Further, the results when changing the dependent variable to job contracts registered in the Ecuadorian Unique Labour system (SUT) offer important insight on the validity of the identification strategy and the robustness of the results. First, a positive post-policy effect is found on all models, and the event study plots show that pre-change dummies are not statistically different from zero except in April 2020, where a strong negative effect is found. After the policy change, month dummies see a progressive increase in their coefficients, however, due to the negative April 2020 coefficient sign, it is policy that the new firms created are not due to the policy but due to catch up effects from the first full lockdown month. The model, however, seems to fit the data in the sense that event-study plots support the empirical strategy and both segmented regressions and month dummy coefficients are negative and statistically significant. This supports the idea that after the policy change and controlling for business creation, jobs decreased.

@@

\section*{Appendix B: Table \ref{tab:regseg}'s results with HAC standard errors}
\label{sec:appb}
\setcounter{table}{0} % reset the table counter
\renewcommand{\thetable}{B.\arabic{table}} % set the table counter to use "A" as the section label
\begin{table}[h]
\caption{Segmented regressions with HAC standard errors}
\label{app:seg}

\begin{tabular}[t]{lcccccc}
\toprule
  & (1) & (2) & (3) & (4) & (5) & (6)\\
\midrule
Time & \num{0.003} & \num{0.000} & \num{0.001}* & \num{-0.004}*** & \num{0.001} & \num{0.001}\\
 & (\num{0.006}) & (\num{0.001}) & (\num{0.000}) & (\num{0.001}) & (\num{0.000}) & (\num{0.001})\\
Time (quadratic) &  &  &  & \num{0.000}*** & \num{0.000} & \num{0.012}***\\
 &  &  &  & (\num{0.000}) & (\num{0.000}) & \vphantom{1} (\num{0.003})\\
Treatment & \num{-0.237}*** & \num{-0.152}*** & \num{-0.120}*** & \num{-0.074}*** & \num{-0.007} & \num{0.031}**\\
 & (\num{0.040}) & (\num{0.022}) & (\num{0.011}) & (\num{0.013}) & (\num{0.006}) & (\num{0.013})\\
Interaction & \num{0.001} & \num{0.003}*** & \num{0.001} &  &  & \\
 & (\num{0.006}) & (\num{0.001}) & (\num{0.001}) &  &  & \\
Interaction (quadratic) &  &  &  & \num{0.000}*** & \num{0.000} & \num{-0.012}***\\
 &  &  &  & (\num{0.000}) & (\num{0.000}) & (\num{0.003})\\
WFH workers &  &  & \num{0.001} & \num{0.001} & \num{0.000} & \num{0.000}\\
 &  &  & (\num{0.002}) & (\num{0.001}) & (\num{0.000}) & (\num{0.001})\\
Thefts &  &  & \num{0.020}* & \num{0.012} & \num{0.008}* & \num{-0.001}\\
 &  &  & (\num{0.011}) & (\num{0.011}) & (\num{0.004}) & (\num{0.006})\\
Homicides &  &  & \num{0.003} & \num{0.002} & \num{0.001} & \num{0.001}\\
 &  &  & (\num{0.003}) & (\num{0.003}) & (\num{0.001}) & (\num{0.002})\\
Tax contributors &  &  & \num{-0.081}* & \num{-0.094}** & \num{-0.041} & \num{-0.095}\\
 &  &  & (\num{0.041}) & (\num{0.040}) & (\num{0.029}) & (\num{0.061})\\
Sales &  &  & \num{0.039}*** & \num{0.033}*** & \num{0.006}* & \num{0.000}\\
 &  &  & (\num{0.011}) & (\num{0.010}) & (\num{0.003}) & (\num{0.004})\\
Transit Accidents &  &  & \num{0.003} & \num{0.002} & \num{-0.001} & \num{-0.002}\\
 &  &  & (\num{0.002}) & (\num{0.002}) & (\num{0.001}) & (\num{0.001})\\
Businesses &  &  &  &  & \num{0.006}*** & \num{0.007}**\\
 &  &  &  &  & (\num{0.002}) & (\num{0.003})\\
Lag of jobs &  &  &  &  & \num{0.942}*** & \num{0.870}***\\
 &  &  &  &  & (\num{0.032}) & (\num{0.058})\\
COVID-19 cases &  &  &  &  &  & \num{0.000}\\
 &  &  &  &  &  & (\num{0.002})\\
COVID-19 deaths &  &  &  &  &  & \num{-0.001}\\
 &  &  &  &  &  & (\num{0.001})\\
Inscriptions &  &  &  &  & \num{0.007}*** & \num{-0.004}\\
 &  &  &  &  & (\num{0.002}) & (\num{0.004})\\
Suspensions &  &  &  &  & \num{0.002} & \num{0.004}\\
 &  &  &  &  & (\num{0.001}) & (\num{0.003})\\
Mobility &  &  &  &  &  & \num{0.000}\\
 &  &  &  &  &  & (\num{0.000})\\
\midrule
$N$ & \num{1327} & \num{1327} & \num{439} & \num{439} & \num{438} & \num{236}\\
Adj. $R^2$ & \num{0.00071} & \num{0.99835} & \num{0.99955} & \num{0.99961} & \num{0.99994} & \num{0.99991}\\
Adj. Within $R^2$ &  & \num{0.46583} & \num{0.74985} & \num{0.77949} & \num{0.96697} & \num{0.85451}\\
AIC & \num{4708.41} & \num{-3771.83} & \num{-1855.13} & \num{-1909.57} & \num{-2732.13} & \num{-1380.83}\\
BIC & \num{4729.17} & \num{-3631.68} & \num{-1736.68} & \num{-1787.04} & \num{-2593.33} & \num{-1263.06}\\
Province FE &  & X & X & X & X & X\\
\bottomrule
\end{tabular}

\end{table}
\clearpage
\section*{Appendix C: Models using SUT job contracts as the explained variable $L_{it}$}
\label{sec:appc}
\renewcommand{\thetable}{C.\arabic{table}}
\setcounter{table}{0} % reset the table counter
